Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-04-01 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex, references] added treatment of B->K* form factors to appendix B and new references for LCSR and lattice calculations

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements.
  Lattice results of $B\to K$ form factors are used to constrain parameters
  of their $q^2$-dependence,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgments}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS} and Chris Bouchard for communications concerning $B\to K$
  form factors \cite{Bouchard:2013eph}.
  C.B. received partial support from the ERC Advanced Grant project ``FLAVOUR''
  (267104).
\end{acknowledgments}

@@

The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ depend on
$B\to K^{(*)}$ form factors and do not receive any other long-distance contribution,
i.e., they factorize naively. These amplitudes are implemented in {\tt EOS} for
$B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as given in \cite{Bobeth:2007dw}
and \cite{Bobeth:2012vn}, respectively, and without the use of form factor relations
at large and low recoil.

\begin{table}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{cccc}
\hline
  Quantity & Prior & Unit & Reference\\
\hline
  \multicolumn{4}{c}{$B\to K$ form factors}\\
\hline
  $f_+(0)$    &  $0.34 \pm 0.05$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $f_T(0)$    &  $0.38 \pm 0.06$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
\hline
  \multicolumn{4}{c}{$B_s$ decay constant}
\\
\hline
  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance parameters
   for hadronic quantities entering inclusive and exclusive decays. Note that
   $f_0(0) = f_+(0)$.
}
\end{center}
\end{table}

As we do not make use of form factor relations for tensorial and scalar amplitudes
in $B\to K\bar\ell\ell$, additional nuisance parameters are included for the complete
set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
$z$-parameterization \cite{Khodjamirian:2010vf}, only five nuisance parameters
(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematical relation
$f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}
and \cite{Ball:2004ye} have been averaged (see \reftab{tab:hadronic:nuisance} and
cf. \cite{Beaujean:2013soa}), and supplemented with lattice determinations~\cite{Bouchard:2013eph}. 
Contrary to \cite{Beaujean:2013soa}, we do not adapt a
log-gamma prior for the asymmetric uncertainties but rather a continuous, but
asymmetric gaussian distribution.
The lattice results are given within a slightly different parameterisation necessitating
a conversion to the parameterisation used here. For this purpose, we generate the
form factors from the parameterisation \cite{Bouchard:2013eph}, including full
correlations, at three values of $q^2 = 17,\, 20,\, 23$ GeV$^2$ finding the results
compiled in \reftab{tab:btok-lattice}. (The $q^2$ values and number of points are chosen
such that the correlation of neighboring points does not exceed $80\%$.)
Subsequently, these ``data'' of the form factors is included in the likelihood
by means of a multivariate Gaussian in addition to experimental measurements.

\begin{table}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccc}
        \hline
        $q^2$ [\GeV] & $17$            & $20$            & $23$\\
        \hline
        $f_0(q^2)$   & $0.62 \pm 0.03$ & $0.72 \pm 0.03$ & $0.87 \pm 0.04$\\
        $f_+(q^2)$   & $1.13 \pm 0.05$ & $1.63 \pm 0.07$ & $2.68 \pm 0.13$\\
        $f_T(q^2)$   & $1.02 \pm 0.06$ & $1.47 \pm 0.08$ & $2.42 \pm 0.18$\\
        \hline
    \end{tabular}\\
    \renewcommand{\arraystretch}{1.0}
    \vspace{2\smallskipamount}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccccccccc}
        \hline
        $q^2$ [\GeV]
             & $17$  & $20$ & $23$ & $17$ & $20$ & $23$ & $17$  & $20$   & $23$ \\
        \hline
   $f_0(17)$ & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010 & 0.048 \\
   $f_0(20)$ & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093 & 0.075 \\
   $f_0(23)$ & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046 & 0.058 \\
   $f_+(17)$ & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21  & 0.051 \\
   $f_+(20)$ & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26  & 0.20  \\
   $f_+(23)$ & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14  & 0.22  \\
   $f_T(17)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79  & 0.46  \\
   $f_T(20)$ & --    & --   & --   & --   & --   & --   & --    & 1.00  & 0.85  \\
   $f_T(23)$ & --    & --   & --   & --   & --   & --   & --    & --    & 1.00  \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Reproduction of mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Bouchard:2013eph} for the
        vector form factors $f_{0,+,T}(q^2)$ in $B\to K$ transitions.
        \label{tab:btok-lattice}
      }
\end{table}

@@

>>>>

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements.
  Lattice results of $B\to K$ form factors are used to constrain parameters
  of their $q^2$-dependence,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.
  \todo{update $B\to K^*$ form factors}
}
\end{center}
\end{table*}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgments}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
  Bouchard and Matthew Wingate for communications on their results of $B\to K$
  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors, 
  respectively. We thank also David Straub for his support with LCSR results of
  $B\to K^*$ form factors \cite{Straub:2015ica}.
  C.B. received partial support from the ERC Advanced Grant project ``FLAVOUR''
  (267104).
\end{acknowledgments}

@@

@@

The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form factors. These amplitudes
are implemented in {\tt EOS} for $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as
given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively. In the case
of $B\to K\bar\ell\ell$, we refrain from using respective form factor relations at
large and low recoil for the tensor and scalar form factors, $f_T$ and $f_0$ in the
corresponding amplitudes. In the case of $B\to K^*\bar\ell\ell$, we use the scalar
form factor $A_0$ in the scalar and time-like amplitudes, but apply form factor
relations in tensor amplitudes for the tensor form factors $T_{1,2,3}$.

\begin{table}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{cccc}
\hline
  Quantity & Prior & Unit & Reference\\
\hline
  \multicolumn{4}{c}{$B_s$ decay constant}
\\
\hline
  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
\hline
  \multicolumn{4}{c}{$B\to K$ form factors}\\
\hline
  $f_+(0)$    &  $0.34 \pm 0.05$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $f_T(0)$    &  $0.38 \pm 0.06$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
\hline
  \multicolumn{4}{c}{$B\to K^*$ form factors}\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance parameters
   for hadronic quantities entering inclusive and exclusive decays. Note that
   $f_0(0) = f_+(0)$.
}
\end{center}
\end{table}

As we do not make use of form factor relations for tensorial and scalar amplitudes
in $B\to K\bar\ell\ell$, additional nuisance parameters are included for the complete
set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
$z$-parameterization \cite{Khodjamirian:2010vf}, only five nuisance parameters
(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematical relation
$f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}
and \cite{Ball:2004ye} have been averaged (see \reftab{tab:hadronic:nuisance} and
cf. \cite{Beaujean:2013soa}), and supplemented with lattice determinations~\cite{Bouchard:2013eph}. 
Contrary to \cite{Beaujean:2013soa}, we do not adapt anymore a log-gamma prior for
the asymmetric uncertainties but rather a continuous, but asymmetric gaussian distribution.
The lattice results are given within a slightly different parameterisation necessitating
a conversion to the parameterisation used here. For this purpose, we generate the
form factors from the parameterisation \cite{Bouchard:2013eph}, including full
correlations, at three values of $q^2 = 17,\, 20,\, 23$ GeV$^2$ finding the results
compiled in \reftab{tab:btok-lattice}. (The $q^2$ values and number of points are chosen
such that the correlation of neighboring points does not exceed $80\%$.)
Subsequently, these ``data'' of the form factors is included in the likelihood
by means of a multivariate Gaussian in addition to experimental measurements.

\begin{table}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccc}
        \hline
        $q^2$ [\GeV$^2$] & $17$            & $20$            & $23$\\
        \hline
        $f_0(q^2)$   & $0.62 \pm 0.03$ & $0.72 \pm 0.03$ & $0.87 \pm 0.04$\\
        $f_+(q^2)$   & $1.13 \pm 0.05$ & $1.63 \pm 0.07$ & $2.68 \pm 0.13$\\
        $f_T(q^2)$   & $1.02 \pm 0.06$ & $1.47 \pm 0.08$ & $2.42 \pm 0.18$\\
        \hline
    \end{tabular}\\
    \renewcommand{\arraystretch}{1.0}
    \vspace{2\smallskipamount}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccccccccc}
        \hline
        $q^2$ [\GeV$^2$]
             & $17$  & $20$ & $23$ & $17$ & $20$ & $23$ & $17$  & $20$   & $23$ \\
        \hline
   $f_0(17)$ & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010 & 0.048 \\
   $f_0(20)$ & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093 & 0.075 \\
   $f_0(23)$ & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046 & 0.058 \\
   $f_+(17)$ & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21  & 0.051 \\
   $f_+(20)$ & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26  & 0.20  \\
   $f_+(23)$ & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14  & 0.22  \\
   $f_T(17)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79  & 0.46  \\
   $f_T(20)$ & --    & --   & --   & --   & --   & --   & --    & 1.00  & 0.85  \\
   $f_T(23)$ & --    & --   & --   & --   & --   & --   & --    & --    & 1.00  \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Reproduction of mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Bouchard:2013eph} for the
        $B\to K$ form factors $f_{0,+,T}(q^2)$.
        \label{tab:btok-lattice}
      }
\end{table}

We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
work \cite{Beaujean:2013soa} slightly and use now the simplified series expansion
(SSE) \cite{Bharucha:2010im}
\begin{align}
  \label{eq:SSE-FF-parameterization}
  F_i(q^2) & =
  \frac{1}{1 - q^2/M_{R,i}^2} \sum_k \alpha_k^i \left[z(q^2) - z(0)\right]^k \,,
\end{align}
with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1}$
and two ($k=1,2$) for $i= A_{12}$. The parameters $\alpha_0^i$ correspond to
$F_i(q^2 = 0)$ and the kinematic constraint
\begin{align}
  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,,
\end{align}
is used to eliminate $\alpha_0^{A_{12}}$, where the kinematic factor 
${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
$B$- and $K^*$-meson masses. The residual masses $M_{R,i}$ are set to the values
given in \cite{Straub:2015ica}.

This parameterization allows us to combine consistently available results
of form factors from different non-perturbative approaches, namely LCSR's at
large recoil and lattice at low recoil and implement simultaneously additional
kinematic constraints. We determine the parameters $\alpha_i^k$
in a combined fit to form factor predictions of $V, A_{0,1,12}$ from the LCSR  
\cite{Straub:2015ica} and lattice \cite{Horgan:2013hoa, Horgan:2015vla} calculations,
including their correlations. Further, we implement the second kinematic constraint 
\begin{align}
  \label{eq:A12-constraint-q2max}
  A_{12}(q_{\rm max}^2) & = {\cal F}_{\rm kin}\, A_1(q_{\rm max}^2)
\end{align}
at maximal $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$. Uninformative flat priors
are chosen for all $\alpha_k^i$
\begin{align}
  \alpha_0^i & \in [0,\, 1] \,, &
  \alpha_{1,2}^i & \in [-10,\, 10].
\end{align}
The results of the LCSR predictions of the form factors have been provided to us
directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12}$, including their $16\times16$
correlation matrix. In the case of lattice predictions, we proceed as in our
previous work \cite{Beaujean:2013soa} by generating form factor values of
$V,\, A_{0,1,12}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
\cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
see \reftab{tab:btokstar-lattice}.

We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
versus two parameters only and found that in the latter case lattice form factor
results influence the fit such that form factors tend to be higher than LCSR
predictions at low $q^2$ leading to a worse fit. Hence we prefer the three-parameter
setup as it accommodates better LCSR and lattice results.

\begin{table}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|cc}
        \hline
        $q^2$ [\GeV$^2$] & $15$            & $19.21$ \\
        \hline
        $V(q^2)$         & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
        $A_0(q^2)$       & $0.62 \pm 0.03$ & $0.72 \pm 0.03$\\
        $A_1(q^2)$       & $1.13 \pm 0.05$ & $1.63 \pm 0.07$\\
        $A_{12}(q^2)$    & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
        \hline
    \end{tabular}\\
    \renewcommand{\arraystretch}{1.0}
    \vspace{2\smallskipamount}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccccccccc}
        \hline
        $q^2$ [\GeV$^2$]
                & $15$  & $19$ & $15$ & $19$ & $15$ & $19$ & $15$  & $19$ \\
        \hline
   $V(15)$      & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010\\
   $V(19)$      & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093\\
   $A_0(15)$    & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046\\
   $A_0(19)$    & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21 \\
   $A_1(15)$    & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26 \\
   $A_1(19)$    & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14 \\
   $A_{12}(15)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79 \\
   $A_{12}(19)$ & --    & --   & --   & --   & --   & --   & --    & 1.00 \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Reproduction of mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Horgan:2015vla} for the
        $B\to K^*$ form factors $V(q^2)$ and $A_{0,1,12}(q^2)$.
        \todo{Enter correct numbers from constraint.cc}
        \label{tab:btokstar-lattice}
      }
\end{table}
